Models

### 2021-10-04 analysis/05_model_metrics.Rmd
Write out csv with study metadata
Include raw metric values

@@

Create dataframe of models to fit
```{r}
raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base"), 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

@@

usethis::use_data(metric_model_table)
pins::pin(metric_model_table, board = "github")
```

#### Process Model Output

>>>>

Write out file with all necessary metadata for the supplement.
```{r}
meta %>% 
  filter(study_id %in% model_data$study_id) %>% 
  select(-c(link_id, date_study_added, sample_desc_name)) %>% 
  write_csv(here::here("paper", "study_metadata.csv"))
```

@@

Create dataframe of models to fit
```{r}
raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "FRic", "FEve", "FDiv", "Jaccard_base"), 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

@@

usethis::use_data(metric_model_table)
pins::pin(metric_model_table, board = "github")
```
#### Process Model Output
